\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-21 chapters/3_algorithm.tex
Update scores and add extended tables

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The average linkage without cannot-link constraints achieved an almost error-free segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

>>>>

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The average linkage without cannot-link constraints returned the best segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

### 2019-05-21 chapters/5_experiments_noise.tex
Update scores and add extended tables

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Rand-Score \\(higher is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Rand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions. On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix \TODO{Table \ref{tab:full_cremi_results}}, \emph{Abs Max} represents a valid and considerably faster option. 
Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.

>>>>

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
DTWS + MC & -& 0.310 \\
DTWS + LMC & -& 0.317 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions. On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix Table \ref{tab:extended_results_cremi}, \emph{Abs Max} represents a valid and considerably faster option. 
Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.

### 2019-05-21 chapters/supplementary.tex
Update scores and add extended tables

\paragraph{Extended results} \TODO{present extended table}

@@

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
% \tilde{F}(x;\theta)=\begin{cases}
% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
% \end{cases}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}). \TODO{Add impl. details}

\begin{figure}[b]
\end{figure}

% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster.}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.6\textwidth}
\centering
        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{minipage}
\end{figure}

>>>>

\paragraph{Extended results} For all algorithms, the chosen value of bias parameter was $\beta = 0$. \TODO{Finish}

\begin{table}[t]
\centering
    \footnotesize
% \begin{minipage}[T]{0.85\textwidth}
%     \centering
        \begin{tabular}{l|c|c|c|c}
          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC & 0.282 & 0.906 & 0.358 & 4.64 $\cdot$ 10$^4$ \\
Abs Max & 0.322 & 0.897 & 0.286 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 6.31 $\cdot$ 10$^4$ \\
Sum & 0.334 & 0.872 & 0.461 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & 0.197 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & 0.197 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cremi}
\end{table}
% \hfill
% \begin{minipage}[T]{0.6\textwidth}
% \centering
%         \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
%     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
%     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
%     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
%     }
%     \label{fig:noisy_affs}
% \end{minipage}
% \end{figure}

@@

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
% \tilde{F}(x;\theta)=\begin{cases}
% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
% \end{cases}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}). \TODO{Add impl. details}
% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
\begin{figure}[t]
\begin{minipage}[T]{0.6\textwidth}
        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
